Towards Explainability of Machine Learning Models in Insurance Pricing

### 2019-11-01 manuscript/manuscript.Rmd
conclusion to present tense

In this paper, we discussed particular questions of model validation that are
of key importance in communicating a model that may present particular
difficulty for machine learning models compared to GLMs or traditional pricing
models. Specifically,

@@

We contextualized these questions in terms of different frameworks for defining
interpretability. We conceptualize interpretability in terms of the ability of
a model (or modeler) to answer a set of idealized questions that would be
refined. We then offered potential (families of) model-agnostic techniques for
providing answers to these questions.

Much work remains to be done in terms of defining the role of machine learning
algorithms in actuarial practice. Lack of interpretability has been a key
barrier preventing wider adoption and exploration of these techniques. The
methods proposed in this paper could therefore represent important strides in
nlocking the potential of machine learning within the insurance industry.

>>>>

In this paper, we discuss particular questions of model validation that are
of key importance in communicating a model that may present particular
difficulty for machine learning models compared to GLMs or traditional pricing
models. Specifically,

@@

We contextualize these questions in terms of different frameworks for defining
interpretability. We conceptualize interpretability in terms of the ability of
a model (or modeler) to answer a set of idealized questions that would be
refined. We then offer potential (families of) model-agnostic techniques for
providing answers to these questions.

Much work remains to be done in terms of defining the role of machine learning
algorithms in actuarial practice. Lack of interpretability has been a key
barrier preventing wider adoption and exploration of these techniques. The
methods proposed in this paper could therefore represent important strides in
unlocking the potential of machine learning within the insurance industry.
